Understanding the impact of electronically-delivered parenting advice

### 2019-01-11 paper/cogsci2019/cogsci2019.Rmd
adding figs

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR)
However, note that TTR is a measure that is correlated with the length of a text. ... 
According to [@Jarvis2010], MTLD is a better measure of lexical diversity.

@@

@@

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also use 
markdown formatting to include footnotes using this syntax [^1].

@@

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

>>>>

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR)
However, note that TTR is a measure that is correlated with the length of a text. ... 
According to Jarvis2010, MTLD is a better measure of lexical diversity.

@@

```{r e2TTR, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "How to do subfigures?"}
img <- png::readPNG("figs/e2_TTR.png")
grid::grid.raster(img)
```

```{r e2MTLD, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/e2_MTLD.png")
grid::grid.raster(img)
```

@@

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. You can also use 
markdown formatting to include footnotes using this syntax [^1].

@@

### 2019-01-11 paper/cogsci2019/cogsci2019.tex
adding figs

@@

@@

\subsubsection{Participants. 84 infants aged 12-24 months and their
parents participated in the same museum as Experiment 1. We included
infants who were exposed to English at least 75 percent of the time or
who were exposed less but whose participating parent reported that they
primarily speak English with their child at home. {[}specific demo
info{]}}\label{participants.-84-infants-aged-12-24-months-and-their-parents-participated-in-the-same-museum-as-experiment-1.-we-included-infants-who-were-exposed-to-english-at-least-75-percent-of-the-time-or-who-were-exposed-less-but-whose-participating-parent-reported-that-they-primarily-speak-english-with-their-child-at-home.-specific-demo-info}

@@

@@

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/2-col-image-1}

\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
\end{figure*}
\end{CodeChunk}

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.04 & 0.11 & 0.3 & 0.74 \\ 
  x & 2.05 & 0.11 & 18.0 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

>>>>

The data was analyzed according to our preregistration. {[}link{]}

@@

\begin{itemize}
\tightlist
\item
  calculate Type/Token Ratio (TTR)
\end{itemize}

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR) However,
note that TTR is a measure that is correlated with the length of a text.
\ldots{} According to Jarvis2010, MTLD is a better measure of lexical
diversity.

@@

\subsubsection{Participants.}\label{participants.-1}

84 infants aged 12-24 months and their parents participated in the same
museum as Experiment 1. We included infants who were exposed to English
at least 75 percent of the time or who were exposed less but whose
participating parent reported that they primarily speak English with
their child at home. {[}specific demo info{]}

@@

{\centering \includegraphics{figs/e2TTR-1}

\caption[How to do subfigures?]{How to do subfigures?}\label{fig:e2TTR}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics{figs/e2MTLD-1}

\caption[One column image]{One column image.}\label{fig:e2MTLD}
\end{figure}
\end{CodeChunk}

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -0.06 & 0.11 & -0.6 & 0.58 \\ 
  x & 2.19 & 0.10 & 21.0 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}
